Group meeting #2

### 2021-11-09 pres/group-meeting2.Rmd
save

[TODO: SHOW RESULTS]

@@

>>>>

### Results of penalization (1/3)

FinnGen sumstats:

```{r, out.width = "75%"}
knitr::include_graphics("regul-finngen.jpg")
```

### Results of penalization (2/3)

Epilepsy sumstats:

```{r, out.width = "75%"}
knitr::include_graphics("regul-epilepsy.jpg")
```

### Results of penalization (3/3)

PAGE sumstats:

```{r, out.width = "75%"}
knitr::include_graphics("regul-page.jpg")
```

@@

- Which alternative weights / method do you find the most interesting?

- How to choose the best penalization? CV did not seem to work
